\ieeetitle

### 2017-01-12 report/ordering.tex
Take into account all remaining comments from Miguel

\subsection{Total Order Algorithms}
A totally ordered set of events is a partially ordered set which satisfies one additional property:
\begin{itemize}
	\item Totality (trichotomy law): For any $a, b \in S$, either $a \leq b$  or $b \leq a$.
\end{itemize}
\par
In other words, total order is an ordering that defines the exact order of every event in the system. On the other hand, partial ordering only defines the order between certain key events that depend on each other. Partial order can be useful since it is less costly to implement. However, in some cases the order of all events is important. For example, imagine we have multiple databases around the world. We want them to appear as if it is only one database. To achieve this, every operation done a particular database would have to be replicated on all the others, we would then have to make sure that every operation is executed in the same order on every database to end up in the same state. However, Total Order is not usually scalable. This lead to the emergence of most of the work on eventual consistency.
\subsection{Related Work}
Related work concerning Total Order is already extensively covered in \autocite{matos2015epto}.

\autocites[]{Chandra2007}[]{Maia2011} each test extensively a different large scale distributed system. However, they do not offer a framework to benchmark different systems than theirs. \autocite{Leonini2009} presents a framework named SPlay to deploy such applications. Unfortunately, SPlay only allows for LUA application. \eptotester offers a convenient framework to deploy distributed applications provided they run in a docker container.

>>>>

\subsection{Total Order Algorithms}
A totally ordered set of events is a partially ordered set which satisfies one additional property:
\begin{itemize}
	\item Totality (trichotomy law): For any $a, b \in S$, either $a \leq b$  or $b \leq a$.
\end{itemize}
\par
In other words, total order is an ordering that defines the exact order of every event in the system. On the other hand, partial ordering only defines the order between certain key events that depend on each other. Partial order can be useful since it is less costly to implement. However, in some cases the order of all events is important. For example, imagine we have multiple databases around the world. We want them to appear as if it is only one database. To achieve this, every operation done a particular database would have to be replicated on all the others, we would then have to make sure that every operation is executed in the same order on every database to end up in the same state. However, Total Order is not usually scalable. This lead to the emergence of most of the work on eventual consistency.

\subsection{\epto Architecture}
\begin{figure}[htp]
	\includegraphics[width=\linewidth]{figures/architecture.pdf}
	\caption{\epto architecture \autocite{matos2015epto}.}
	\label{fig:epto-architecture}
\end{figure}
\autoref{fig:epto-architecture} illustrates the architecture of a single \epto replica. An application extending our Application class can \epto-broadcast and \epto-deliver events. Events broadcasted to the Dissemination component are sent over the network every $\delta$ period, where $\delta$ is a unit of time. Every ball received from the network is unwrapped and its events are analyzed by the dissemination component to find out whether they need to be propagated further or not according to their Time To Live (TTL). They are then sent to the ordering component so that \epto can determine whether to deliver these events or not and in which order. The order is based on the \textit{timestamp} of the events given by the logical clock and their \textit{broadcasterID} in case of a tie. The network layer is managed by \eptotester.
\subsection{Related Work}
Related work concerning Total Order is already extensively covered in \autocite{matos2015epto}.

Both \autocite{Chandra2007} and \autocite{Maia2011} extensively test a particular large scale distributed system. However, they do not offer a framework to benchmark different systems. \autocite{Leonini2009} presents a framework named SPlay to deploy such applications. Unfortunately, SPlay only allows for LUA applications to run. \eptotester offers a convenient framework to deploy distributed applications regardless of the programming language used, provided they run in a docker container .
